% Back matter adapted from cancer-automated/papers/VVUQ-02/final-paper:
% Acknowledgments, Ethical Disclosures, Rights and Permissions, Cite This
% Article, Data Availability. Each is added to the table of contents.

\bmhead{Acknowledgments}
The author acknowledges Anthropic for access to Claude Code regarding the instruction,
drafting, and assembly of this narrative review; OpenAI for ChatGPT subject
support; and Google Gemini for assistance.

\bmhead{Ethical Disclosures}
The author declares no competing interests. This is an independent narrative
review and is not endorsed, sponsored, or approved by any trial sponsor, CRO,
site, IRB, regulator, or medical society, nor by CFR, ICH, or FDA. H. R. 9510 is
an illustrative bill number; it is not enacted law and this review is not legal
advice. All supporting numbers are simulation or illustrative results unless tied
to a cited source.

\bmhead{Rights and Permissions}
This review is distributed under the Creative Commons Attribution 4.0
International License (CC BY 4.0). To view a copy, visit
\url{https://creativecommons.org/licenses/by/4.0/}. Reproduced public-domain U.S.
Government text is used under 17 U.S.C. \S~105.

\bmhead{Cite This Review}
Kawchak K. From H. R. 9510 to Federal Law: A Narrative Case for Verified Physical AI Oncology Trials. Zenodo. 2026;
\href{https://doi.org/10.5281/zenodo.20685379}{10.5281/zenodo.20685379}.

\bmhead{Data Availability}
All sources, figures, and prompt records supporting this review are openly
available for download in the kevinkawchak/law-physical-ai-trials repository under review/ (the prompt, the four sub-prompts, the colored Mermaid catalog,
as well as the AI generated draft, full, and final paper stages), which draw on the public records in kevinkawchak/single-prompt-bill, kevinkawchak/cancer-automated, kevinkawchak/Clinical-AI-Demos, and the author's Zenodo deposits.\ All data
sets are synthetic or illustrative; no patient-identifiable information is
included.
