\section{Urgency: patients are waiting now}
\label{sec:urgency}

The final appeal is timing. Legislation accelerates when delay is shown to have a
cost: patients are waiting now, lives are being lost now, and the technology is
advancing faster than the rules that govern it. But urgency must be handled with
care. Research on fear appeals finds that they motivate action only when the
audience also believes a solution is within reach; a catastrophe presented without
a credible remedy tends to paralyze rather than move \cite{kok2013finding}. So this
section pairs the pressure of time with a remedy already in hand.

The gap is real. Capability, in the form of Physical AI, surgical humanoids, and
autonomous pipelines, is rising quickly, while regulation, built for an earlier
era and supplemented mainly by guidance, lags behind \cite{fda2021samd}. The
distance between the two curves is where preventable harm accumulates.
Figure 11 shows the gap and the single instrument that closes it.

\begin{narrativefig}
\node[nftwo] (c1) at (0,0) {Physical AI}; \node[nftwo] (c2) at (3.2,0) {Surgical humanoids};
\node[nftwo] (c3) at (6.4,0) {Autonomous pipelines};
\node[nfone] (r1) at (0,-1.6) {Legacy rules}; \node[nfone] (r2) at (3.2,-1.6) {Guidance only};
\node[nfrisk] (r3) at (6.4,-1.6) {Regulation gap};
\node[nfact] (act) at (9.6,-0.8) {H. R. 9510};
\node[nfhope] (g) at (12.4,-0.8) {Patients protected now};
\draw[nfedge] (c1)--(c2); \draw[nfedge] (c2)--(c3); \draw[nfedge] (r1)--(r2); \draw[nfedge] (r2)--(r3);
\draw[nfedge] (c3) to[out=0,in=120] (act.north);
\draw[nfedge] (r3) to[out=0,in=-120] (act.south);
\draw[nfedge] (act)--(g);
\end{narrativefig}
\vspace{-0.15cm}
\figcaption{Figure 11. Closing the capability-regulation gap (Mermaid 16 and 21 as
colored TikZ): the Act is the bridge that joins fast-moving capability to
lagging rules.}

\autoref{tab:urgency} sets the cost of another year of delay against the cost of
acting, so the urgency points toward a decision rather than toward despair.

\begin{table}[H]
\footnotesize
\begin{tabularx}{\textwidth}{@{}L{4.4cm} Y@{}}
\toprule
\textbf{Dimension} & \textbf{Effect of one more year}\\
\midrule
Patients waiting & Trial access delayed for those with the least time\\
Preventable harm & Unverified tools deployed without a gate\\
Public trust & Skepticism hardens without a transparent record\\
Cost of acting & Bounded, authorized, and budget-scored in the bill\\
\bottomrule
\end{tabularx}
\caption{The cost of delay against the bounded cost of acting.}
\label{tab:urgency}
\end{table}

The eight appeals converge on one request. The evidence exists, the tools are
tested, the safeguards are written, and the people are waiting. We therefore ask
the committee to enact H. R. 9510 (v5.0) into Federal law
\cite{Kawchak2026HR9510Bill}. The quiet questions, asked eight times, resolve into
a single answer: we no longer have to carry this task with unaided human attention,
and we should not ask patients to wait while we decide to stop.
